Creating optimal conditions for reproducible data analysis in R with \pkg{fertile}

### 2020-01-03 fertile_sdss.Rnw
fixed LaTeX error

The \cmd{proj_analyze()}function creates a report documenting the structure of a data analysis project. This report contains informations about all packages referenced in code; the files present in the directory, and their types; suggestions for moving files to create a more organized structure; and a list of reproducibility-breaking file paths used in code.

@@

In addition to the primary reproducability analsis functions present in \cmd{check}, \cmd{proj_analyze}, and the interactive warning system, several useful utility functions are made available to \pkg{fertile} users. Among other things, these include functions to check the type of a file and a way to create a copy of a project in a temp directory.

>>>>

The \cmd{proj\_analyze()} function creates a report documenting the structure of a data analysis project. This report contains informations about all packages referenced in code; the files present in the directory, and their types; suggestions for moving files to create a more organized structure; and a list of reproducibility-breaking file paths used in code.

@@

In addition to the primary reproducability analsis functions present in \cmd{check}, \cmd{proj\_analyze()}, and the interactive warning system, several useful utility functions are made available to \pkg{fertile} users. Among other things, these include functions to check the type of a file and a way to create a copy of a project in a temp directory.
